Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-22 writing/embedded_meta_learning_appendix.tex
Part II

\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_i\right), \mathcal{T}\left(y_i\right) \right) \text{ for } (x_i, y_i) \in D_1 \right\}\right)\right)\]

@@

\[\mathbb{E}_{(z_{source}, z_{target})\in {D}_2} \left[ \mathfrak{L}\left(z_{target}, f_{D_1}\left(\mathcal{I} \left(z_{source}\right)\right) \right)\right]\]
where $\mathfrak{L}$ is $\ell_2$ loss, and $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]

>>>>

\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
where $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_i\right), \mathcal{T}\left(y_i\right) \right) \text{ for } (x_i, y_i) \in D_1 \right\}\right)\right)\]

@@

\[\mathbb{E}_{(z_{source}, z_{target})\in {D}_2} \left[ \mathfrak{L}\left(z_{target}, F_{D_1}\left(\mathcal{I} \left(z_{source}\right)\right) \right)\right]\]
where $\mathfrak{L}$ is $\ell_2$ loss, and $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
